### 2020-09-08 latex/vlp.tex
Inserted the vlp T/smooth controllers
Inserted the VNHC injection/dissipation image

\section{The VLP Constraint}
% TODO: Go through the development of the constraint and prove it gains energy
% TODO: Explain how we came up with the constraint first. Talk about the child
% on a swing, the paper showing the time-optimal control input, and describe why
% we want to remove time from the equation. Discuss the lmin and lmax choices.
% Why do we need to use a VNHC instead of a VHC: we are modelling the
% time-optimal controller in a time-independent way, which requires knowledge of
% which quadrant in (q,p)-space we're in. This means using the angle theta,
% which is inherently a VNHC.
Since we wish to define a VNHC which injects energy into the VLP in a human-like
manner,
we return once again to the example of a person standing on a swing.
As can be seen in Figure \ref{fig:child-vlp}, condensing the person 
into a center of mass gives a VLP model of their motion, where
the pendulum shrinks when the person stands and lengthens when they squat. This
is equivalent to the VLP model from Figure \ref{fig:vlp-model}.
\begin{figure}
   \centering
   \begin{subfigure}[t]{0.45\textwidth}
      \includegraphics[]{images/child_vlp_standing.png}
      \caption{A person standing on a swing has their center of mass 
      close to the pivot.}
   \end{subfigure}
   \hfill
   \begin{subfigure}[t]{0.45\textwidth}
      \includegraphics[]{images/child_vlp_squatting.png}
      \caption{When a person squats on a swing, their center of mass extends
      away from the pivot.}
   \end{subfigure}
   \caption{The variable length pendulum representation of a person on a
   standing swing.}\label{fig:child-vlp}
\end{figure}

@@

\begin{figure}
   \centering
   \includestandalone[width=0.6\textwidth]{images/vlp_T_controller}
   \caption{The continuous VNHC-style VLP controller \(l_T(\theta)\).}\label{fig:vlp-T-controller}
\end{figure}

@@

\begin{figure}
   \centering
   % TODO: Insert the image of the smoothed VLP controller around lavg
   \caption{The smoothed VLP controller attained by setting the parameter 
      \(T\) to its upper limit
   \(\frac{\pi}{2}\).}\label{fig:vlp-smoothed-controller}
\end{figure}

@@

\begin{figure}
   \centering
   % TODO: Add a figure showing regions for injection vs dissipation
   \caption{}\label{fig:vlp-energy-in-out}
\end{figure}

>>>>

\section{The VLP Constraint}
% Go through the development of the constraint and prove it gains energy
Since we wish to define a VNHC which injects energy into the VLP in a human-like
manner,
we return once again to the example of a person standing on a swing.
As can be seen in Figure \ref{fig:child-vlp}, condensing the person 
into a center of mass gives a VLP model of their motion, where
the pendulum shrinks when the person stands and lengthens when they squat. This
is equivalent to the VLP model from Figure \ref{fig:vlp-model}.
\begin{figure}
   \centering
   \begin{subfigure}[t]{0.45\textwidth}
      \includegraphics[]{images/child_vlp_standing.png}
      \caption{A person standing on a swing has their center of mass 
      close to the pivot.}
   \end{subfigure}
   \hfill
   \begin{subfigure}[t]{0.45\textwidth}
      \includegraphics[]{images/child_vlp_squatting.png}
      \caption{When a person squats on a swing, their center of mass extends
      away from the pivot.}
   \end{subfigure}
   \caption{The variable length pendulum representation of a person on a
   standing swing.}\label{fig:child-vlp}
\end{figure}

@@

\begin{figure}
   \centering
   \includestandalone[width=0.7\textwidth]{images/vlp_T_controller}
   \caption{The continuous VNHC-style VLP controller \(l_T(\theta)\).}\label{fig:vlp-T-controller}
\end{figure}

@@

\begin{figure}
   \centering
   \includestandalone[width=0.8\textwidth]{images/vlp_smoothed_controller}
   \caption{The smoothed VLP controller which corresponds to the VNHC \(l =
      l_\frac{\pi}{2}(\theta)\).}\label{fig:vlp-smoothed-controller}
\end{figure}

@@

\begin{figure}
   \centering
   \includestandalone[width=0.5\textwidth]{images/vlp_energy_in_out}
   \caption{A VNHC of the form \(l(\theta)\) which is entirely contained within
      the green (yellow) regions will inject (dissipate) energy into the VLP
      because it will satisfy Theorem \ref{thm:vlp-energy-stabilization}.}
      \label{fig:vlp-energy-in-out}
\end{figure}
